The human in the loop: volunteer-based metacomputers as a socio-technical system

### 2016-04-24 Alife16/paper.tex
Revising the SoS
Closes #115

JavaScript can be used for either unwitting
\citep{unwitting-ec,boldrin2007distributed} or volunteer
\citep{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\citep{Desell:2008:AHG:1389095.1389273,duda2013distributed,DBLP:journals/corr/abs-0801-1210}. Many
other researchers have used Java \citep{chong:1999:jDGPi}; others have
embraced peer to peer systems
\citep{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These
computing platforms avoid single points of failure (the server) and
once installed need no effort to gather new users for an experiment,
but the cost of acquiring new users is high since they need to be set
up.

>>>>

JavaScript can be used for either unwitting
\citep{unwitting-ec,boldrin2007distributed} or volunteer
\citep{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\citep{Desell:2008:AHG:1389095.1389273,duda2013distributed,DBLP:journals/corr/abs-0801-1210}. Many
other researchers have used Java \citep{chong:1999:jDGPi}; others have
embraced peer to peer systems
\citep{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These
computing platforms avoid single points of failure, the server, and
once installed need no effort to gather new users for an experiment,
but the cost of acquiring new users is high since they need to be set
up.
